Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-31 EconGrowth.Rnw
Added a predGDP title to the column of predictions.

@@

<<CD Lattice Graph>>=
usModel <- cobbDouglasModel("US")
coefs <- coef(usModel)
print(coef(usModel))
usPred <- predict(usModel)
class(usPred)
print(usPred)
data.frame(usPred)

@

>>>>

#########################
# Takes the Cobb-Douglas fitted models and creates per-country predictions for them.
# Returns a data.frame with the predictions.
##
cobbDouglasPredictions <- function(countryName){
  model <- cobbDouglasModel(countryName)
  coefs <- coef(usModel)
  pred <- predict(model) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
  return(data.frame(pred))
}

#########################
# Takes the Cobb-Douglas fitted models and creates a single column of predicted GDP values
# that corresponds to the AllData.txt file.
##
cobbDouglasPredictionsColumn <- function(){
  preds <- lapply(countries, cobbDouglasPredictions)
  out <- rbind(preds[["US"]], preds[["UK"]], preds[["JP"]], preds[["CN"]], preds[["ZA"]], preds[["SA"]], preds[["IR"]], preds[["TZ"]], preds[["ZM"]])
  colnames(out) <- c("predGDP")
  print(out)
  return(out)
}

@@

<<CD Lattice Graph>>=
usModel <- cobbDouglasModel("US")
coefs <- coef(usModel)
# print(coef(usModel))
usPred <- predict(usModel) #See http://stackoverflow.com/questions/9918807/how-get-plot-from-nls-in-r
class(usPred)
#print(usPred)
data.frame(usPred)

allData <- loadData("All")
predictions <- cobbDouglasPredictionsColumn()
allData <- cbind(allData, predictions)

print(allData)
@
